Empty Homes V1

### 2017-05-29 EmptyHomesV1.Rmd
Corplotter
Added in the function that plots corellations of two variables. It is useful for reducing the code spaghetti that was forming as these plots are useful for inspecting relationships.

#Haringey is funney and has to be worked over a bit first
Haringeyinfo <- read.xlsx("Haringey_Exemptions_Discounts_LSOA.xlsx")[c(1,3,5)]

@@

@@

ChelseaCor <- Chelseainfo %>% 
  summarise(x =cor(MedianPrice, WardLowUsePerc, use = 'complete.obs'))

 Chelseainfo %>% ggplot(., aes(y=MedianPrice, x= WardLowUsePerc )) + geom_point() +
   labs(title = "Median Price vs Low Use % by ward in RBKC",
        x = "Low Use Percentage by Ward", 
        y = "Median Price") +
  theme(plot.title = element_text(hjust = 0.5)) + 
    annotate("text", 
             label = paste0("Correlation = ", 
             signif(ChelseaCor[1,1],2)), 
             x = 5 , y = 3.5e5, size = 5) +
   geom_smooth(method = "lm", se = FALSE)
SaveFig("ChelseaCor.png")

@@

CornCor <- Cornwall %>% 
  #filter(Admin_ward_code !="E05009195") %>% 
  summarise(x =cor(MedianPrice, WardLowUsePerc, use = 'complete.obs'))

 Cornwall %>% ggplot(., aes(y=MedianPrice, x= WardLowUsePerc )) + geom_point() +
   labs(title = "Mean Price vs Low Use % by ward in Cornwall",
        x = "Low Use Percentage by Ward", 
        y = "Mean Price") +
  theme(plot.title = element_text(hjust = 0.5)) + 
    annotate("text", 
             label = paste0("Correlation = ", signif(CornCor[1,1],2)), 
             x = 5 , y = 3.5e5, size = 5) +
   geom_smooth(method = "lm", se = FALSE)
SaveFig("CornCor.png")

@@

test <-read_excel(file.path(RegionsComp, "Region Yorkshire and The Humber",
                "KINGSTON UPON HULL%2c CITY OFDISCOUNTSLSOA.XLSX"))[-c(c(1:6)),1:4] %>%
  StructureData(.)

PlotMap(test, AG, variable = "WardLowUsePerc")

>>>>

#Haringey is funny and has to be worked over a bit first
Haringeyinfo <- read.xlsx("Haringey_Exemptions_Discounts_LSOA.xlsx")[c(1,3,5)]

@@

PlotMap(Lambethinfo, AG, title = "Low-use homes in Kensington and Chelsea")

Chelseainfo %>% mutate(Value = ValLow/1e6) %>%
  PlotMap(., AG, variable = "Value", title = "Low-use homes in Kensington and Chelsea")

@@

corplotter(Chelseainfo, "MedianPrice", "WardLowUsePerc", "Median Price vs Low Use % by ward in RBKC",
           "Low Use Percentage by Ward",
           "Median Price")
SaveFig("ChelseaCor.png")

@@

corplotter(Cornwall, "MedianPrice", "WardLowUsePerc", 
           "Median Price vs Low Use % by ward in Cornwall",
           "Low Use Percentage by Ward",
           "Median Price")
SaveFig("CornCor.png")

@@

Hull <-read_excel(file.path(RegionsComp, "Region Yorkshire and The Humber",
                "KINGSTON UPON HULL%2c CITY OFDISCOUNTSLSOA.XLSX"))[-c(c(1:6)),1:4] %>%
  StructureData(.)

PlotMap(Hull, AG, variable = "WardLowUsePerc")

corplotter(Hull, "MedianPrice", "WardLowUsePerc", 
           "Median Price vs Low Use % by ward in Hull",
           "Low Use Percentage by Ward",
           "Median Price")
```
